Reading Notes

### 2020-08-14 2pd.tex
added hexane xml
oops--wrong smarts string

%%\begin{wrapfigure}{L}{0.6\textwidth}
%%    \centering
%%    \includegraphics[width=0.5\textwidth]{images/hexanexml.pdf}
%%    \caption{XML file used by VOTCA to specify a three site coarse grain mapping of n-hexane}
%%    \label{fig:hexanexml}
%%\end{wrapfigure}

It may be easy to think that because what we are doing--mapping two carbons and their attached hydrogens to a single bead so that six alkyl carbons becomes A-B-A--that the process will also be simple.
In order to specify a bead-mapping, we need to know the residue number, the residue name, and the atom name.
For a six atom system this is not too bad, but this could get tedious and error-prone for larger systems.
And keep in mind that these xml files need to be created manually for each compound which is backmapped.
VOTCA's scheme also requires that you specify the bonding and the angles resulting from those bonds, another process which is tedious, error-prone, and probably unecessary--I will discuss this more after discussing my scheme below:
\begin{lstlisting}
hexane_sites = [("_A", "CC[H3]"), ("_B", "CC")]
\end{lstlisting}
The result of using this code in the `coarse` function %%<link to grits> is a three-site hexane model A-B-A, same as VOTCA.
The mapping here is specified as a list of bead name / smarts string pairs.
Although they do add some element of cognitive load, SMARTS strings are designed to be human and machine readable and can match atoms based on their chemical environment.
With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (CC) requiring that one be a terminal carbon by including that it has three attached hydrogens (C[H3]).
The bonding and angles of the resulting coarse grain beads is then inferred based on the bonding of the mapped atoms.
Basically what VOTCA's xml file does in 51 lines, I can do in 1 which is easier to read and makes chemical sense. 
There are even benefits to the mapping being inline with the code:
This allows the user to see the mapping as they progress through the workflow without having to search for multiple files and it may prevent common errors caused by manual file IO such as operating system specific line endings or whitespace characters like tab or space being treated differently.
Having the mapping in-line with the workflow also allows for the user to check that the mapping is correct with built in interactive visualizations, which can display the mapping as an overlay. %%<show overlay>

>>>>

\begin{wrapfigure}{L}{0.5\linewidth}
    \centering
    \includegraphics[width=0.6\linewidth]{images/hexanexml.pdf}
    \caption{XML file used by VOTCA to specify a three site coarse grain mapping of n-hexane}
    \label{fig:hexanexml}
\end{wrapfigure}

It may be easy to think that because what we are doing--mapping two carbons and their attached hydrogens to a single bead so that six alkyl carbons becomes A-B-A--that the process will also be simple.
In order to specify a bead-mapping, we need to know the residue number, the residue name, and the atom name.
For a six atom system this is not too bad, but this could get tedious and error-prone for larger systems.
And keep in mind that these xml files need to be created manually for each compound which is backmapped.
VOTCA's scheme also requires that you specify the bonding and the angles resulting from those bonds, another process which is tedious, error-prone, and probably unecessary--I will discuss this more after discussing my scheme below:
\begin{lstlisting}
hexane_sites = [("_A", "C[CH3]"), ("_B", "CC")]
\end{lstlisting}
The result of using this code in the `coarse` function is a three-site hexane model A-B-A, same as VOTCA.%%<link to grits>
The mapping here is specified as a list of bead name / smarts string pairs.
Although they do add some element of cognitive load, SMARTS strings are designed to be human and machine readable and can match atoms based on their chemical environment.
With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (using the SMARTS string "CC") and requiring that one be a terminal carbon by including that it has three attached hydrogens ("[CH3]").
The order of the beads here matters--because technically all atoms could be mapped with the more general SMARTS string (CC), it is important to list the most specific strings first.
The bonding and angles of the resulting coarse grain beads is then inferred based on the bonding of the mapped atoms.
Basically what VOTCA's xml file does in 51 lines, I can do in 1 which is easier to read and makes chemical sense. 
There are even benefits to the mapping being inline with the code:
This allows the user to see the mapping as they progress through the workflow without having to search for multiple files and it may prevent common errors caused by manual file IO such as operating system specific line endings or whitespace characters like tab or space being treated differently.
Having the mapping in-line with the workflow also allows for the user to check that the mapping is correct with built in interactive visualizations, which can display the mapping as an overlay. %%<show overlay>
